Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-27 src/tex/ms.tex
[showyourwork] overleaf sync

\section{}
\label{sec: correlations}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/correlation_high_mass_slope_SN_delay.pdf}
    \vspace{-.5cm}
    \caption{.}
    \label{fig:correlation}
    \script{plot_sbc.py}
\end{figure*}

>>>>

\section{Correlation analysis of inference results}
\label{sec: correlations}
In order to characterize the relation between the global parameters $\alpha_{\text{IMF}}$ and $\log_{10} N_{\text{Ia}}$, we have decided to study the correlation obtained from the inference results on the whole validation set. Figure \ref{fig:corner_plot} display a possible positive correlation, and in order to obtain a population level statics of this results, we calculate for each star in the validation set the 2x2 covariance matrix\footnote{We have used only the global parameters components of the sample to calculate the covariance matrix.} of the posterior samples, extracting the off diagonal value. In Figure \ref{fig:correlation}, the histogram of the correlation value is shown, and all the inference results suggest a positive correlation. We kept only the left sided 99 percentile for graphical reasons, but also those removed outliers are in agreement with the conclusion. 
We checked the independence of this results from the accuracy of the inference with the central and right plots of Fig. \ref{fig:correlation}.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/correlation_high_mass_slope_SN_delay.pdf}
    \vspace{-.5cm}
    \caption{The left Figure shows the distribution of the correlation between the global parameters $\alpha_{\text{IMF}}$ and $\log_{10} N_{\text{Ia}}$, obtained by the covariance matrix of the sample of each star in the validation set. The central and right Figures show the correlation as a function of the Euclidean and Mahalanobis distance of the true value $\theta_{\text{true}}$ and the sample average $\theta_{\text{predicted}}$. This results shows that the correlation is independent on the accuracy of the inference.}

    \label{fig:correlation}
    \script{plot_sbc.py}
\end{figure*}
